---
title: "Introduction_oncoCluster"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_oncoCluster}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

oncoCluster is an R package which identifies cancer subtypes using DNA 
methylation data. It employs different clustering algorithms and allows users to
compare the results. There are also functions to visualise the results and 
compare the output of the analysis.


## Installation

```{r setup}
require(devtools)
install_github("ShahzadaShameelFarooq/oncoCluster", build_vignettes = TRUE)
library(oncoCluster)
```

To list all sample functions available in the package:
``` r
ls("package:oncoCluster")
```
To list all sample datasets available in the package:
``` r
data(package = "oncoCluster")
```

## Using the functions

An example function call to clusterAnalysis and clusterPlot
```{r, }
# Dna methylation Data of multiple patients 
dim(methylationData)

# DNA methylation sites deemed significant for clustering by cox regression
dim(significantSites)

# Function call to clusterAnalysis
res <- clusterAnalysis(dnaMethylationData = methylationData, dnaMethylationSites = significantSites)

# View the results of clusterAnalysis
res

# Create a plot of the results
clusterPlot(dnaMethylationData = methylationData,
dnaMethylationSites = significantSites, clusterResults = res)
```

An example function call to clusterAnalysisTwo and clusterPlot
```{r, }
# Dna methylation Data of multiple patients 
dim(methylationData)

# DNA methylation sites deemed significant for clustering by cox regression
dim(significantSites)

# Function call to clusterAnalysisTwo
resTwo <- clusterAnalysisTwo(dnaMethylationData = methylationData, dnaMethylationSites = significantSites)

# View the results of clusterAnalysisTwo
resTwo

# Viewing the classification of the results from clusterAnalysisTwo
resTwo$classification

# Create a plot of the results
clusterPlot(dnaMethylationData = methylationData,
dnaMethylationSites = significantSites, clusterResults = resTwo)
```

An example function call to clusterComparison
```{r, }
# Dna methylation Data of multiple patients 
dim(methylationData)

# DNA methylation sites deemed significant for clustering by cox regression
dim(significantSites)

# Perform clustering using both clusterAnalysis and clusterAnalysisTwo
resOne <- clusterAnalysis(dnaMethylationData = methylationData, dnaMethylationSites = significantSites)
resTwo <- clusterAnalysisTwo(dnaMethylationData = methylationData, dnaMethylationSites = significantSites)

# Function call to clusterComparison

finalRes <- clusterComparison(clusterAnalysisRes = resOne, clusterAnalysisTwoRes = resTwo)

# View the result
finalRes


```

An example function call to compareClusterPlot
```{r,}
results <- clusterAnalysis(dnaMethylationData = methylationData, dnaMethylationSites = significantSites)
resultsTwo <- clusterAnalysisTwo(dnaMethylationData = methylationData, dnaMethylationSites = significantSites)

compareClusterPlot(clusterResults = results, clusterResultsTwo = resultsTwo)
```

## Package References

- Farooq, S.M.S. (2022) oncoCluster: R package to identify cancer sub-types 
  through clustering and DNA methylation Data.
  
## Other references

R Core Team (2021). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. https://www.R-project.org/

H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York,
  2016.

Wickham H, François R, Henry L, Müller K (2022). _dplyr: A Grammar of Data
  Manipulation_. R package version 1.0.10,
  <https://CRAN.R-project.org/package=dplyr>.

Kassambara A, Mundt F (2020). _factoextra: Extract and Visualize the Results of
  Multivariate Data Analyses_. R package version 1.0.7,
  <https://CRAN.R-project.org/package=factoextra>.
  
Li, T., Chen, X., Gu, M. et al. Identification of the subtypes of gastric
cancer based on DNA methylation and the prediction of prognosis.
Clin Epigenet 12, 161 (2020). https://doi.org/10.1186/s13148-020-00940-3

Scrucca L., Fop M., Murphy T. B. and Raftery A. E. (2016) mclust 5: clustering, classification and
density estimation using Gaussian finite mixture models The R Journal 8/1, pp. 289-317

```{r}
sessionInfo()
```

