---
title: "Introduction_oncoCluster"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_oncoCluster}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

oncoCluster is an R package which uses single omics and multi-omics data to 
identify cancer sub-types by using various clustering algorithms. It also allows
the user to visualize the results of the clustering algorithms by creating plots.


## Installation

```{r setup}
require(devtools)
install_github("ShahzadaShameelFarooq/oncoCluster", build_vignettes = TRUE)
library(oncoCluster)
```

To list all sample functions available in the package:
``` r
ls("package:oncoCluster")
```
To list all sample datasets available in the package:
``` r
data(package = "oncoCluster")
```

## Using the functions

An example function call to clusterAnalysis and clusterPlot
```r
# Dna methylation Data of multiple patients 
dim(methylationData)

# DNA methylation sites deemed significant for clustering by cox regression
dim(significantSites)

# Function call to clusterAnalysis
res <- clusterAnalysis(dnaMethylationData = methylationData, dnaMethylationSites = significantSites)

# View the results of clusterAnalysis
res

# Create a plot of the results
clusterPlot(dnaMethylationData = methylationData,
dnaMethylationSites = significantSites, clusterResults = res)
```


